ms_figures

### 2023-01-17 ms_figures.Rmd
new ms figures pipeline

```{r load_database_data}
# Load ARTIS data from SQL local database
con <- dbConnect(RPostgres::Postgres(),
                 dbname=Sys.getenv("POSTGRES_DB"),
                 host="localhost",
                 port="5432",
                 user=Sys.getenv("POSTGRES_USER"),
                 password=Sys.getenv("POSTGRES_PASSWORD"))

# Check that connection is established by checking which tables are present
dbListTables(con)

# Pull all ARTIS and production data
artis <- dbGetQuery(con, "SELECT * FROM snet")

artis <- artis %>%
  select(-record_id)

prod <- dbGetQuery(con, "SELECT * FROM production")
prod <- prod %>%
  select(-record_id)

country_metadata <- dbGetQuery(con, "SELECT * FROM countries")
country_metadata <- country_metadata %>%
  select(-record_id)

code_max_resolved_taxa <- dbGetQuery(con, "SELECT * FROM code_max_resolved_taxa") %>%
              mutate(hs6 = as.character(hs6)) %>%
  select(-record_id)

sciname_metadata <- dbGetQuery(con, "SELECT * FROM sciname") %>%
  select(-record_id)

# Close database connection
dbDisconnect(con)

rm(list = c("con"))
```

```{r set_directories}
# Set time series dates
date_nodash <- "20220926"
date_dash <- "2022-09-26"

# Set directories 
outdir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization"

# Set color palettes
# All colors from palette: #FFE6BE (light yellow), #F7AF75 (light orange), #F37542 (medium orange), 
# #E24027 (dark orange), #0F2D59 (navy), #1B708F (blue), #2E8D9A (teal), #86ADA7 (light blue)
method_colors <- c("#F7AF75", "#2E8D9A", "#86ADA7") # light orange, teal, light blue
source_colors <- c("#F37542", "#0F2D59", "#86ADA7") # medium orange, navy, light blue
environment_colors <- c( "#2E8D9A", "#0F2D59","#86ADA7") # teal, navy, light blue

@@

```{r join_data}
# Summarize cleaned FAO production data
prod <- prod %>% 
  select("year", "iso3c", "sciname", 
         "method", "habitat", 
         "production_t" = "live_weight_t") %>%
  group_by(year, iso3c, sciname, method, habitat) %>%
  summarise(production_t = sum(production_t, na.rm = TRUE)) %>%
  ungroup()

# Join production data to ARTIS
artis <- artis %>%
  filter(live_weight_t >= 0.1) %>%
  # Add importer and exporter region
  left_join(country_metadata %>% 
              select("exporter_iso3c" = "iso3c", "exporter_region" = "owid_region"), by = c("exporter_iso3c")) %>%
  left_join(country_metadata %>% 
              select("importer_iso3c" = "iso3c", "importer_region" = "owid_region"), by = c("importer_iso3c")) %>%
# FIX IT: Determine if this should be deleted. Production of only species exports may not be relevant
  left_join(prod, by = c("year", "exporter_iso3c" = "iso3c", 
                           "sciname", "method", "habitat")) %>%
  ungroup()

# Update artis data to lowest resolution by comparing code taxa_level and prod taxa_level
artis <- artis %>%
  left_join(code_max_resolved_taxa,
            by = c("hs_version", "hs6", "sciname")) %>%
  left_join(sciname_metadata, 
            by = "sciname") %>%
  # Leave any missing sciname_hs_modified as original sciname
  mutate(sciname_hs_modified = case_when(
    is.na(sciname_hs_modified) ~ sciname,
    TRUE ~ sciname_hs_modified
  )) %>%
  rename(environment = habitat) %>%
  # Add habitat-method column
  mutate(habitat_method = paste(environment, method, sep =" ")) %>% 
  mutate(habitat_method = case_when(
    str_detect(habitat_method, "unknown") ~ "unknown", 
    TRUE ~ habitat_method
  )) %>% 
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" )))

# Remove data frames after merged with ARTIS
rm(list = c("code_max_resolved_taxa", "sciname_metadata"))

@@

```{r fig1a}
global_export_by_source <- artis %>% 
  mutate(food_or_fmfo = case_when(
    hs6 == "230120" ~ "fishmeal",
    hs6 != "230120" ~ "nonfishmeal"
  )) %>%
  group_by(year, habitat_method, food_or_fmfo) %>%
  summarise(live_weight_t = sum(live_weight_t))

write.csv(global_export_by_source, "outputs/global_export_by_source.csv", row.names = FALSE)

fig1a <- global_export_by_source %>%
  group_by(year, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(y = "Exports (mil. t, live weight)", fill = "Source", x = "") +
  theme_bw() +
  theme(legend.position = "bottom")

@@

```{r fig1b}
prod_by_source <- prod %>%
  group_by(year, method, habitat) %>% 
  summarise(production_t = sum(production_t)) %>%
  mutate(habitat_method = paste(habitat, method, sep = " ")) %>%
    # Set factor levels
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture",
                                            "marine aquaculture", "inland aquaculture"))) %>%
  ungroup() %>%
  select(-habitat, -method)

dom_export_by_source <- artis %>% 
  filter(dom_source == "domestic export") %>%
  group_by(year, habitat_method, environment) %>%
  summarise(dom_live_weight_t = sum(live_weight_t))

percent_export_by_source <- dom_export_by_source %>%
  left_join(prod_by_source, by = c("year", "habitat_method")) %>% 
  mutate(percent_export = 100*dom_live_weight_t/production_t)

write.csv(percent_export_by_source, "outputs/percent_export_by_source_summary.csv", row.names = FALSE)

percent_export_total <- dom_export_by_source %>%
  left_join(prod_by_source, by = c("year", "habitat_method")) %>% 
  group_by(year) %>% 
  summarise(dom_live_weight_t = sum(dom_live_weight_t), 
            production_t = sum(production_t)) %>%
  mutate(percent_export = 100*dom_live_weight_t/production_t) %>% 
  mutate(calc_type = "domestic exports") %>% 
  select(year, percent_export, calc_type)

percent_export_total_all_source <- artis %>% 
  group_by(year) %>% 
  summarise(live_weight_t = sum(live_weight_t)) %>%
  left_join(prod_by_source %>% 
              group_by(year) %>% 
              summarise(production_t = sum(production_t)), 
            by = c("year")) %>% 
  mutate(percent_export = 100*live_weight_t/production_t) %>% 
  mutate(calc_type = "all export sources") %>% 
  select(year, percent_export, calc_type)

percent_export_total <- percent_export_total %>%
  bind_rows(percent_export_total_all_source)

write.csv(percent_export_total, "outputs/percent_export_total_summary.csv", row.names = FALSE)

fig1b <- ggplot() +
  geom_line(data = percent_export_by_source, aes(x = year, y = percent_export, color = habitat_method)) +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "% production exported", x = "", color = "Source") +
  theme_bw()

@@

```{r fig1c}
all_degree_summary <-  artis %>% 
  select(year, exporter_iso3c, importer_iso3c) %>%
  distinct() %>%
  group_by(year, exporter_iso3c) %>%
  tally() %>% 
  rename(all_out_degree = n, iso3c = exporter_iso3c) %>%
  full_join(artis %>% 
              select(year, exporter_iso3c, importer_iso3c) %>%
              distinct() %>%
              group_by(year, importer_iso3c) %>%
              tally() %>%
              rename(all_in_degree = n, iso3c = importer_iso3c), 
            by = c("year", "iso3c"))

write.csv(all_degree_summary, "outputs/all_degree_summary.csv", row.names = FALSE)

habitat_method_degree_summary <-  artis %>% 
  select(year, exporter_iso3c, importer_iso3c, habitat_method) %>%
  distinct() %>%
  group_by(year, exporter_iso3c, habitat_method) %>%
  tally() %>% 
  rename(all_out_degree = n, iso3c = exporter_iso3c) %>%
  full_join(artis %>% 
              select(year, exporter_iso3c, importer_iso3c, habitat_method) %>%
              distinct() %>%
              group_by(year, importer_iso3c, habitat_method) %>%
              tally() %>%
              rename(all_in_degree = n, iso3c = importer_iso3c), 
            by = c("year", "iso3c", "habitat_method"))

write.csv(habitat_method_degree_summary, "outputs/habitat_method_degree_summary.csv", row.names = FALSE)

fig1c_out_degree <- artis %>% 
  filter(habitat_method != "unknown") %>%
  select(year, exporter_iso3c, importer_iso3c, habitat_method) %>%
  distinct() %>%
  group_by(year, exporter_iso3c, habitat_method) %>%
  tally() %>%
  group_by(year, habitat_method) %>%
  ggplot(aes(x = year, y = n, color = habitat_method)) +
  geom_smooth() +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "Out degree", fill = "Source") + 
  theme_bw()

fig1c_in_degree <- artis %>% 
  filter(habitat_method != "unknown") %>%
  select(year, exporter_iso3c, importer_iso3c, habitat_method) %>%
  distinct() %>%
  group_by(year, importer_iso3c, habitat_method) %>%
  tally() %>%
  group_by(year, habitat_method) %>%
  ggplot(aes(x = year, y = n, color = habitat_method)) +
  geom_smooth() +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "In degree", fill = "Source") + 
  theme_bw()

```{r fig1, fig.height = 3, fig.width = 4.5}
png("outputs/fig1.png")
ggarrange(fig1a,
          ggarrange(fig1b,
                    fig1c_out_degree,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("b", "c")),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 2, labels = c("a", ""))

dev.off()
```

@@

```{r SI_top_capture_aqua_imp_exp, fig.height=4, fig.width=4}
# Summarize total imports and exports by habitat and environment
bilateral_habitat_method_summary <- artis %>%
  # Remove if we decide to leave FMFO in
  filter(hs6 != "230120") %>%
  group_by(year, exporter_iso3c, exporter_region, importer_iso3c, importer_region, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t))

write.csv(bilateral_habitat_method_summary, "outputs/bilateral_habitat_method_summary.csv", row.names = FALSE)

top_traders_recent <- bilateral_habitat_method_summary %>% 
  filter(year %in% 2016:2020, habitat_method != "unknown") %>%
  group_by(importer_iso3c, exporter_iso3c, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(2016:2020))

top_importers_recent <- top_traders_recent %>%
  group_by(importer_iso3c, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  group_by(habitat_method) %>%
  slice_max(n = 10, order_by = live_weight_t) %>%
  ungroup() %>%
  group_by(habitat_method) %>%
  mutate(ranking = rank(live_weight_t)) %>%
  ungroup() %>%
  mutate(importer_iso3c = reorder_within(importer_iso3c, ranking, habitat_method)) %>%
  ggplot(aes(x = live_weight_t/1000000, y = importer_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

top_exporters_recent <- top_traders_recent %>%
  group_by(exporter_iso3c, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  group_by(habitat_method) %>%
  slice_max(n = 10, order_by = live_weight_t) %>%
  ungroup() %>%
  group_by(habitat_method) %>%
  mutate(ranking = rank(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter_iso3c = reorder_within(exporter_iso3c, ranking, habitat_method)) %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

ggarrange(top_exporters_recent, top_importers_recent, ncol = 2, labels = c("Export", "Import"))

top_traders_past <- bilateral_habitat_method_summary %>% 
  filter(year %in% 1996:2000, habitat_method != "unknown") %>%
  group_by(importer_iso3c, exporter_iso3c, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)/length(1996:2000))

top_importers_past <- top_traders_past %>%
  group_by(importer_iso3c, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  group_by(habitat_method) %>%
  slice_max(n = 10, order_by = live_weight_t) %>%
  ungroup() %>%
  group_by(habitat_method) %>%
  mutate(ranking = rank(live_weight_t)) %>%
  ungroup() %>%
  mutate(importer_iso3c = reorder_within(importer_iso3c, ranking, habitat_method)) %>%
  ggplot(aes(x = live_weight_t/1000000, y = importer_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

top_exporters_past <- top_traders_past %>%
  group_by(exporter_iso3c, habitat_method) %>%
  summarise(live_weight_t = sum(live_weight_t)) %>%
  group_by(habitat_method) %>%
  slice_max(n = 10, order_by = live_weight_t) %>%
  ungroup() %>%
  group_by(habitat_method) %>%
  mutate(ranking = rank(live_weight_t)) %>%
  ungroup() %>%
  mutate(exporter_iso3c = reorder_within(exporter_iso3c, ranking, habitat_method)) %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

ggarrange(top_exporters_past, top_importers_past, ncol = 2, labels = c("Export", "Import"))

# Largest export increases
top_exporter_change <- bilateral_habitat_method_summary %>% 
  filter(year %in% c(1996:2000, 2016:2020)) %>%
  mutate(year_group = case_when(
    year %in% 1996:2000 ~ "beginning", 
    year %in% 2016:2020 ~ "end")) %>%
  group_by(year_group, exporter_iso3c, habitat_method) %>% 
  summarise(live_weight_t = sum(live_weight_t)) %>%
  pivot_wider(names_from = year_group, values_from = live_weight_t) %>% 
  mutate(change = end-beginning) %>% 
  arrange(desc(change))

# Largest increases
top_export_increases <- top_exporter_change %>% 
  filter(habitat_method != "unknown") %>%
  ungroup() %>%
  group_by(habitat_method) %>%
  slice_max(n = 10, order_by = change) %>%
  ungroup() %>%
  mutate(exporter_iso3c = reorder_within(exporter_iso3c, change, habitat_method)) %>%
  ggplot(aes(x = change/1000000, y = exporter_iso3c, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=exporter_iso3c, yend=exporter_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

# Largest decreases
top_export_decreases <- top_exporter_change %>% 
  filter(habitat_method != "unknown") %>%
  ungroup() %>%
  group_by(habitat_method) %>%
  slice_min(n = 10, order_by = change) %>%
  ungroup() %>%
  mutate(exporter_iso3c = reorder_within(exporter_iso3c, change, habitat_method)) %>%
  ggplot(aes(x = change/1000000, y = exporter_iso3c, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=exporter_iso3c, yend=exporter_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

ggarrange(top_export_decreases, top_export_increases, nrow = 1)

# Largest import increases
top_importer_change <- bilateral_habitat_method_summary %>% 
  filter(year %in% c(1996:2000, 2016:2020)) %>%
  mutate(year_group = case_when(
    year %in% 1996:2000 ~ "beginning", 
    year %in% 2016:2020 ~ "end")) %>%
  group_by(year_group, importer_iso3c, habitat_method) %>% 
  summarise(live_weight_t = sum(live_weight_t)) %>%
  pivot_wider(names_from = year_group, values_from = live_weight_t) %>% 
  mutate(change = end-beginning) %>% 
  arrange(desc(change))

# Largest increases
top_import_increases <-top_importer_change %>% 
  filter(habitat_method != "unknown") %>%
  ungroup() %>%
  group_by(habitat_method) %>%
  slice_max(n = 10, order_by = change) %>%
  ungroup() %>%
  mutate(importer_iso3c = reorder_within(importer_iso3c, change, habitat_method)) %>%
  ggplot(aes(x = change/1000000, y = importer_iso3c, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=importer_iso3c, yend=importer_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

# Largest decreases
top_import_decreases <-top_importer_change %>% 
  filter(habitat_method != "unknown") %>%
  ungroup() %>%
  group_by(habitat_method) %>%
  slice_min(n = 10, order_by = change) %>%
  ungroup() %>%
  mutate(importer_iso3c = reorder_within(importer_iso3c, change, habitat_method)) %>%
  ggplot(aes(x = change/1000000, y = importer_iso3c, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=importer_iso3c, yend=importer_iso3c)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

ggarrange(top_import_decreases, top_import_increases, nrow = 1)

# Repeat for regional trends
# Largest export increases
top_exporter_change <- bilateral_habitat_method_summary %>% 
  filter(year %in% c(1996:2000, 2016:2020)) %>%
  mutate(year_group = case_when(
    year %in% 1996:2000 ~ "beginning", 
    year %in% 2016:2020 ~ "end")) %>%
  group_by(year_group, exporter_region, habitat_method) %>% 
  summarise(live_weight_t = sum(live_weight_t)) %>%
  pivot_wider(names_from = year_group, values_from = live_weight_t) %>% 
  mutate(change = end-beginning) %>% 
  arrange(desc(change))

# Largest increases
top_region_export <- top_exporter_change %>% 
  filter(habitat_method != "unknown") %>%
  ungroup() %>%
  group_by(habitat_method) %>%
  slice_max(n = 10, order_by = change) %>%
  ungroup() %>%
  mutate(exporter_region = reorder_within(exporter_region, change, habitat_method)) %>%
  ggplot(aes(x = change/1000000, y = exporter_region, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=exporter_region, yend=exporter_region)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

>>>>

```{r load_data}
# Set directories
datadir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization/20220111"
outdir <- "/Volumes/jgephart/ARTIS/Outputs/ms_seafood_globalization/outputs_20220111"

```{r color_palettes}
# Set color palettes
# All colors from palette: #FFE6BE (light yellow), #F7AF75 (light orange), #F37542 (medium orange), 
# #E24027 (dark orange), #0F2D59 (navy), #1B708F (blue), #2E8D9A (teal), #86ADA7 (light blue)
method_colors <- c("#F7AF75", "#2E8D9A", "#86ADA7") # light orange, teal, light blue
source_colors <- c("#F37542", "#0F2D59", "#86ADA7") # medium orange, navy, light blue
environment_colors <- c( "#2E8D9A", "#0F2D59","#86ADA7") # teal, navy, light blue

@@

@@

```{r fig1a}
fig1a_data <- read.csv(file.path(datadir, "fig_1a_data.csv"))

fig1a <- fig1a_data %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(y = "Exports (mil. t, live weight)", fill = "Source", x = "") +
  theme_bw() +
  theme(legend.position = "bottom")

fig1a
```

@@

```{r fig1b}
fig1b_data <- read.csv(file.path(datadir, "fig_1b_data.csv"))

fig1b <- ggplot() +
  geom_line(data = percent_export_by_source, aes(x = year, y = percent_export, color = habitat_method)) +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "% Production Exported", x = "", color = "Source") +
  theme_bw()

fig1b
```

@@

```{r fig1c}
fig1c_data <- read.csv(file.path(datadir, "fig_1c_data.csv"))

fig1c_out_degree <- fig1c_data %>%
  ggplot(aes(x = year, y = all_in_degree, color = habitat_method)) +
  geom_smooth() +
  scale_color_manual(values = habitat_source_colors) +
  labs(y = "Out degree", color = "Source") + 
  theme_bw()

fig1c_out_degree
```

```{r fig1, fig.height = 3, fig.width = 4.5}
ggarrange(fig1a,
          ggarrange(fig1b,
                    fig1c_out_degree,
                    ncol = 2, nrow = 1,
                    legend = "none",
                    labels = c("b", "c")),
          common.legend = TRUE, legend = "bottom",
          ncol = 1, nrow = 2, labels = c("a", ""))

ggsave(file.path(outdir, "fig1.png"))
```

@@

```{r fig2_data}
artis_region_method <- read.csv(file.path(datadir, "artis_region_method.csv"))
artis_region <- read.csv(file.path(datadir, "artis_region.csv"))
```

```{r fig2a}
# Imports by Region
fig2a <- artis_region %>% 
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = exporter_region)) +
  geom_area() +
  labs(x = "", y = "", fill = "Exporter") +
  scale_fill_manual(values = region_colors) +
  facet_wrap(~importer_region, nrow = 1) +
  theme_bw() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.text.x = element_blank(),
        plot.margin=unit(c(0.5,0,0,0), "cm"))

fig2a
```

```{r fig2b}
# Matrix of plots showcasing inter-regional trade trends
fig2b <- artis_region_method %>% 
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(x = "", y = "Trade (million t, live weight)", color = "Ave. annual change in export \n(1000 t live weight)") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), 
        legend.position = "none",
        strip.background = element_blank(),
        plot.margin=unit(c(0,0,0,0), "cm")) +
  facet_grid(rows = vars(exporter_region), cols = vars(importer_region), 
             labeller = label_wrap_gen(width = 5), scales = "free")

fig2b
```

```{r fig 2c}
# Figure 2c
# Exports by Region
fig2c <- artis_region %>% 
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = importer_region)) +
  geom_area() +
  labs(x = "", y = "", fill = "Importer") +
  scale_fill_manual(values = region_colors) +
  facet_wrap(~exporter_region, ncol = 1) +
  theme_bw() +
  theme(legend.position = "none",
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
        plot.margin=unit(c(0,0.5,0,0), "cm"))

fig2c
```

```{r fig2}
# Overall Figure 2
ggarrange(ggarrange(fig2a, NULL,
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 1.25), labels = c("a", "")),
          ggarrange(fig2b, 
                    ggarrange(NULL, fig2c,
                              ncol = 1, heights = c(0.3, 4)), 
                    ncol = 2, nrow = 1,
                    widths = c(4.5, 1), labels = c("b", "c")),
          ncol = 1, nrow = 2, 
          heights = c(1, 4.5))

ggsave(file.path(outdir, "fig2.png"))
```

# Figure 3
```{r fig3a}
# Global per capita supply
fig3a_data <- read.csv(file.path(datadir, "fig3a_data.csv"))

fig3a <- fig3a_data %>%
  ggplot(aes(x = year, y = supply_per_cap, color = habitat_method)) +
  geom_line() + 
  labs(y = "Per capita supply (kg)", x = "", color = "Source") +
  scale_color_manual(values = habitat_source_colors) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

fig3a
```

```{r fig3b}
# Per capita supply by region
fig3b_data <- read.csv(file.path(datadir, "fig3b_data.csv"))

fig3b <- fig3b_data %>%
  ggplot(aes(x = year, y = supply_per_cap, fill = habitat_method)) +
  geom_area() + 
  labs(y = "Per capita supply (kg)", x = "", fill = "Source") +
  scale_fill_manual(values = habitat_source_colors) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~region)

fig3b
```

```{r fig3c}
# Global percent of supply by domestic / foreign exports
fig3c_data <- read.csv(file.path(datadir, "fig3c_data.csv"))

fig3c <- fig3c_data %>%
  ggplot(aes(x = year, y = supply_percent, color = supply_source)) +
  geom_line() +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

fig3c
```

```{r fig3d}
fig3d_data <- read.csv(file.path(datadir, "fig3d_data.csv"))

fig3d <- fig3d_data %>%
  ggplot(aes(x = year, y = supply_percent, color = supply_source)) +
  geom_line() +
  scale_color_manual(values = c("#F37542", "#0F2D59")) +
  labs(x = "", y = "Percent of supply", color = "Origin") +
  facet_wrap(~region) +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

fig3d
```

```{r fig3}
fig3 <- ggarrange(
  ggarrange(fig3a, fig3b, 
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("a", "b")),
  ggarrange(fig3c, fig3d,
            common.legend = TRUE, nrow = 1, widths = c(1, 2),
            labels = c("c", "d")),
  nrow = 2
)

fig3

ggsave(file.path(outdir, "fig3.png"))
```

```{r fig4a}
fig4a_data <- read.csv(file.path(datadir, "figa4a_data.csv"))

fig4a <- fig4a_data %>%
  ggplot(aes(x = year, y = shannon, color = source)) +
  geom_line() +
  scale_color_manual(values = c(c("#F37542", "#0F2D59"))) +
  labs(x = "", y = "Shannon index", color = "") +
  theme_minimal() +
  theme(legend.position = "bottom",
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_wrap(~region)

fig4a
```

```{r fig4b}
fig4b_data <- read.csv(file.path(datadir, "fig4b_data.csv"))

fig4b <- fig4b_data %>%
  ggplot(aes(x = shannon_supply_domestic, y = shannon_supply_foreign, color = region)) +
    geom_point(alpha = 0.7) +
    geom_abline(slope = 1, intercept = 0) +
  scale_color_manual(values = region_colors) +
  labs(x = "Domestic supply diversity", 
       y = "Foreign supply diversity",
       color = "") +
    theme_minimal()

fig4b
```

```{r fig4c}
fig4c_data <- read.csv(file.path(datadir, "fig4c_data.csv"))

fig4c <- fig4c_data %>%
  ggplot(aes(x = imports_live_weight_t/1000000, y = shannon_supply_no_error, color = region)) +
  geom_point(alpha = 0.7) +
  scale_x_log10() +
  scale_color_manual(values = region_colors) +
  theme_minimal() +
  labs(x = "Total imports (million t, live weight)",
       y = "Supply diversity",
       color = "")

fig4c
```
```{r fig4, fig.height = 3, fig.width = 3}
fig4 <- ggarrange(fig4a, 
          ggarrange(fig4b,
                    fig4c,
                    nrow = 1,
                    common.legend = TRUE, 
                    legend = "bottom",
                    labels = c("b", "c")),
          nrow = 2,
          labels = c("a", "", "")
          )

fig4
```

# Supplementary Figures

```{r si_top_exporters, fig.height = 4, fig.width = 4}

top_exporters_old <- read.csv(file.path(datadir, "top_exporters_old.csv"), row.names = FALSE)
top_exporters_recent <- read.csv(file.path(datadir, "top_exporters_recent.csv"), row.names = FALSE)

exporters_old_plot <- top_exporters_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

exporters_recent_plot <- top_exporters_recent %>%
  ggplot(aes(x = live_weight_t/1000000, y = exporter_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

ggarrange(
  exporters_old_plot,
  exporters_recent_plot,
  ncol = 2,
  labels = c("Old", "Recent")
)

ggsave(file.path(outdir, "si_top_exporters.png"))
```

```{r si_top_importers, fig.height = 4, fig.width = 4}

top_importers_old <- read.csv(file.path(datadir, "top_importers_old.csv"), row.names = FALSE)
top_importers_recent <- read.csv(file.path(datadir, "top_importers_recent.csv"), row.names = FALSE)

importers_old_plot <- top_importers_old %>%
  ggplot(aes(x = live_weight_t/1000000, y = importer_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

importers_recent_plot <- top_importers_recent %>%
  ggplot(aes(x = live_weight_t/1000000, y = importer_iso3c, fill = habitat_method)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

ggarrange(
  importers_old_plot,
  importers_recent_plot,
  ncol = 2,
  labels = c("Old", "Recent")
)

ggsave(file.path(outdir, "si_top_importers.png"))
```

```{r si_regional_changes, fig.height = 4, fig.width = 4}

# Largest regional export changes
top_regional_export_change <- read.csv(file.path(datadir, "top_regional_export_change.csv"))

regional_export_change_plot <- top_regional_export_change %>%
  ggplot(aes(x = change/1000000, y = exporter_region, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=exporter_region, yend=exporter_region)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

# Largest regional import changes
top_regional_import_change <- read.csv(file.path(datadir, "top_regional_import_change.csv"))

regional_import_change_plot <- top_regional_import_change %>%
  ggplot(aes(x = change/1000000, y = importer_region, fill = habitat_method, color = habitat_method)) +
  geom_segment(aes(x=0, xend=change/1000000, y=importer_region, yend=importer_region)) +
  geom_point(size=4) +
  scale_color_manual(values = habitat_source_colors) +
  scale_y_reordered() +
  labs(y = "", x = "Live weight (million t)") +
  facet_wrap(~habitat_method, ncol = 1, scales = "free_y") +
  theme_minimal() +
  theme(legend.position = "none")

ggarrange(
  regional_export_change_plot,
  regional_import_change_plot,
  ncol = 2,
  labels = c("Export", "Import")
)

ggsave(file.path(outdir, "regional_changes.png"))
```

```{r si_export_decreases_increases, fig.height = 4, fig.width = 4}
top_exporter_increases <- read.csv(file.path(datadir, "top_export_increases.csv"))
top_exporter_decreases <- read.csv(file.path(datadir, "top_export_decreases.csv"))
